Social Patriotism

### 2016-02-15 writing_in_ethics/paper_two.tex
finish paper two

It appears that under Kantian analysis, many of the actions taken by the FBI are unethical. The Patriot Act allows for the government to interfere with the lives of the American population with little regard for the law, but the legality of an action does not necessarily determine whether that action is ethically right or wrong.  It is hard to say whether or not the Patriot Act itself is ethical or not, but many of the ways in which law enforcement has interpreted and used it are unethical. 
\end{linenumbers}
\newpage
\nocite{*}
\printbibliography
\end{document}

>>>>

It appears that under Kantian analysis, many of the actions taken by the FBI are unethical. The Patriot Act allows for the government to interfere with the lives of the American population with little regard for the law, but the legality of an action does not necessarily determine whether that action is ethically right or wrong. It is hard to say whether or not the Patriot Act itself is ethical or not; Kantian ethics do however focus on the morality of a decision. The Patriot Act was put in place to protect the citizens of the United States, which Kant would argue is a morally right cause. Many of the actions taken by the FBI in the name of the Patriot Act were presumably done for the same reason, but there is no way to know for certain. 
\end{linenumbers}
\newpage
\nocite{*}
\printbibliography
\end{document}
